Computational tools for representation theory of affine Lie algebras

### 2009-07-22 AffineLieAlgebras/ACMS2009/article.tex
Some text on anomalous branching coefficients and weight multiplicities

We are mostly interested in the use of the new method proposed in the papers
\cite{lyakhovsky1996rra,lyakhovsky2007dub,ilyin812pbc,kulish4sfa}. The
idea is to use recurrent relations for anomalous branching
coefficients based on the summation over the special
set of vectors $\Gamma_{\frak{a}\subset \frak{g}} $ called ``fan''.
\begin{equation}
  \label{recurrent-relation}
  k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
    \sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
      \left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
      \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
      +\gamma }^{\left( \mu \right) }\right)   
\end{equation}

>>>>

We are mostly interested in the use of the new method proposed in the papers
\cite{lyakhovsky1996rra,lyakhovsky2007dub,ilyin812pbc,kulish4sfa}. The
idea is to use recurrent relations for anomalous branching
coefficients based on the summation over the special
set of vectors $\Gamma_{\frak{a}\subset \frak{g}} $ called ``fan''. We
need to introduce some notations. Let's consider the reduction of the
representation of the affine Lie algebra $\mathfrak{g}$ to 
representations of affine Lie algebra $\mathfrak{a}$. By
$\pi_{\mathfrak{a}}$ we denote the projection of the root space
$\frak{h}_{\frak{g}}^{\ast }$ to $\frak{h}_{\frak{a}}^{\ast }$. The
set $\Gamma_{\frak{a}\subset \frak{g}} $ is introduced as the
combination of projection of positive roots $\Delta^{+}$ of algebra
$\frak{g}$ using formulae:
\begin{equation}
  \label{eq:7}
  \prod_{\alpha \in \left( \pi _{\frak{a}}\circ \Delta ^{+}\right) }\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset 
      \frak{g}}}s\left( \gamma \right) e^{-\gamma }.  
\end{equation}
\begin{equation}
\label{eq:18}
  \Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
      \gamma \right) \neq 0\right\} ;  
\end{equation}

\begin{equation}
\label{eq:19}
  \Gamma_{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
      \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
\end{equation}

\begin{equation}
  \label{recurrent-relation}
  k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
    \sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
      \left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
      \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
      +\gamma }^{\left( \mu \right) }\right)   
\end{equation}
